The role of viscosity on drop impact forces

### 2024-08-27 Rebuttal.R2/Response to Reviewer 2.tex

	\item[$\bullet$] \textit{3.}
	\begin{itemize}
		\renewcommand\labelitemi{--}
		\item \textit{In the experimental methods, the authors now describe that the Bond number is fixed at 1. Given the change in fluid properties between different solutions (with fixed droplet size), this cannot be the case. This needs to be made more precise. Furthermore, in the authors' prior work (Zhang et al. (2022)), it is mentioned that the Bo is fixed at 0.5 in simulation for similar experimental parameters. Why the change?}

		\VS{To discuss: The results are Bond invariant in the leading order. Therefore, we chose a representative value of Bond = 1: this if for a diameter $0.00256\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, acceleration due to gravity $10\,\si{\meter/\second^2}$, surface tension $0.06\,\si{\newton/\meter}$. The dimensionless number that matter is the Froude number $Fr = V^2/gD_0 = We/Bo$ which is larger than 1 throughout the paper. The difference as compared to \citet{zhang2022impact} is in the length scale (2 mm in PRL and 2.56 mm in this work).}

		\item \textit{By now providing the drop size used, the Oh and Bo now can be used to define the parameters. However, it is not clear that the non-dimensional values are correct. For instance, Figures 2 and 3 both mention experimental conditions where Oh = 0.0025 whereas apparently different droplet sizes were used (2.05 mm in Figure 2, and 2.54 mm in Figure 3). Was a different fluid used between these figures such that the Oh could be held fixed? To clarify all of these issues, and for the ease of the readers, I strongly suggest the authors add the dimensional parameters for all experiments to the captions (as they have now done for Figure 2), an appendix, or make experimental data available in a supplementary data set.}

		\item \textit{Given the significant amount of data overlap in the various figures (e.g. Figure 3(b)), I am more convinced now that the parameters and raw data need to be provided in a supplementary dataset for reproducibility and to facilitate further comparisons.}\\[2mm]

### 2024-08-27 Main/ViscousDropImpact_v7.tex
feat: Update Force2_Anatomy_v4.pdf and respond to Reviewer 2
The changes made in this commit include:

1. Update the metadata of the Force2_Anatomy_v4.pdf file, including the "xmptk" and "Length" values.
2. Update the contents of the Force2_Anatomy_v4.pdf file, specifically removing several PDF objects that are no longer needed.
3. Add a new PDF file, "Rebuttal.R2/Response to Reviewer 2.pdf", which likely contains the response to the comments from Reviewer 2.

These changes were made to address feedback from Reviewer 2 and to optimize the PDF file for the project.

In the experimental setup, shown schematically in figure~\ref{fig:schematic}(a), a liquid drop impacts a superhydrophobic substrate. For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}. On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}. 
The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}. Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}. The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle. Throughout this work, we use drops with diameter $2.54 \pm 0.02\,\si{\milli\meter}$ unless otherwise stated. Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~\eqref{Eq:OhDefinition}). The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate. 
All experiments are conducted at ambient pressure and temperature. The impact force is directly measured using a high-precision piezoelectric force transducer (Kistler 9215A) with a resolution of $0.5\,\si{\milli\newton}$. During these measurements, the high-frequency vibrations induced by the measurement system and the surrounding noise are spectrally removed using a low pass filter with a cut-off frequency of $5\,\si{\kilo\hertz}$, following the procedure in \citet{Li2014, Zhang2017, Gordillo2018, Mitchell2019}. 
The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$. \Rev{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size. We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.}

@@

This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
The drop diameter determination involved multiple steps. First, we measured the total mass ($M_{100}$) of 100 drops using an electric balance. From this mass, the drop density, and assuming spherical shape, we calculated the drop diameter ($D_0$). We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$. The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
For impact velocity determination, we extracted data from experimental high-speed imagery. By tracking the drop center's position in successive frames prior to substrate contact, and knowing the frame rate, we calculated the impact velocity. We repeated this process for five trials, obtaining $V_{0,1}$ through $V_{0,5}$. The average of these values gave the final impact velocity ($V_0$) and its standard error.

The standard errors for drop diameters did not exceed $0.13\,\si{\milli\meter}$. For drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$, the diameters were $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively. 
The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$. For the same Oh values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
The combined errors in $D_0$ and $V_0$ resulted in approximately $\pm 7\%$ error in Weber number $We$ and $\pm 3\%$ error in Ohnesorge number $Oh$. Consequently, the horizontal error bars, which relate to errors in the control parameters, are smaller than the symbol sizes in our figures.
\bb

>>>>

In the experimental setup, shown schematically in figure~\ref{fig:schematic}(a), a liquid drop impacts a superhydrophobic substrate. For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}. On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}. 
The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}. Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}. The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle \oo (see appendix~\ref{app:error} for details).\bb\,
Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~\eqref{Eq:OhDefinition}). The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate. 
All experiments are conducted at ambient pressure and temperature. The impact force is directly measured using a high-precision piezoelectric force transducer (Kistler 9215A) with a resolution of $0.5\,\si{\milli\newton}$. During these measurements, the high-frequency vibrations induced by the measurement system and the surrounding noise are spectrally removed using a low pass filter with a cut-off frequency of $5\,\si{\kilo\hertz}$, following the procedure in \citet{Li2014, Zhang2017, Gordillo2018, Mitchell2019}. 
The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$. \Rev{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size. We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.}

@@

This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
The drop diameter determination involves multiple steps. First, we measure the total mass ($M_{100}$) of 100 drops using an electric balance. From this mass, using the liquid density and assuming spherical shape, we calculated the drop diameter ($D_0$). 
We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$. The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
For impact velocity determination, we extracted data from experimental high-speed imagery. By tracking the drop center's position in successive frames prior to substrate contact, and knowing the frame rate, we calculated the impact velocity. We repeated this process for five trials, obtaining $V_{0,1}$ through $V_{0,5}$. The average of these values gave the final impact velocity ($V_0$) and its standard error.

The standard errors for drop diameters do not exceed $0.13\,\si{\milli\meter}$. For instance, drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively. 
The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$. For the same Oh values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
The combined errors in $D_0$ and $V_0$ resulted in approximately $\pm 7\%$ error in Weber number $We$ and $\pm 3\%$ error in Ohnesorge number $Oh$. Consequently, the horizontal error bars, which relate to errors in the control parameters, are smaller than the symbol sizes in our figures.
\bb
